He-Man: A domain-specific language for lightweight concurrency

### 2012-03-05 paper/paper.tex
tweak

\title{He-Man: A domain-specific language for lightweight concurrency}
%\subtitle{I said hey, what's goin' on}
\authorinfo{Carlo Angiuli}{}{cangiuli@cs.cmu.edu}
\authorinfo{Michael Sullivan}{}{mjsulliv@andrew.cmu.edu}
\date{December 12, 2011}

@@

We present He-Man, a compiled, embedded, domain specific language in Haskell for
building scalable network applications in a natural, straight-line manner while
still producing efficient event loop-based code. He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
\url{https://github.com/msullivan/networks-project}.
\end{abstract}

@@

%% XXX: do wereally want to talk about this?
As of version 2.5.44, Linux has supported \t{epoll} for non-blocking
multiplexing I/O. A server can register any number of file descriptors with
\t{epoll\_ctl}, and a call to \t{epoll\_wait} returns the ready descriptors.

@@

The latest version of He-Man can be found at
\url{https://github.com/msullivan/networks-project}.

>>>>

\title{He-Man: A domain-specific language for lightweight concurrency}
%\subtitle{I said hey, what's goin' on}
\authorinfo{Carlo Angiuli}{Carnegie Mellon University}{cangiuli@cs.cmu.edu}
\authorinfo{Michael Sullivan}{Carnegie Mellon University}{mjsulliv@cs.cmu.edu}

@@

We present He-Man, a compiled, embedded, domain specific language in Haskell for
building scalable network applications in a natural, straight-line manner while
still producing efficient event loop-based code. He-Man programs are compact and
measurements indicate that it performs acceptably. Our implementation is
available at
\url{https://github.com/msullivan/he-man}.
\end{abstract}

@@

%% XXX: do we really want to talk about this?
As of version 2.5.44, Linux has supported \t{epoll} for non-blocking
multiplexing I/O. A server can register any number of file descriptors with
\t{epoll\_ctl}, and a call to \t{epoll\_wait} returns the ready descriptors.

@@

The latest version of He-Man can be found at
\url{https://github.com/msullivan/he-man}.
